\documentclass[letterpaper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.38in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{array}
\usepackage{titlesec}

\pagestyle{empty}
\urlstyle{same}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\tabcolsep}{0pt}

\newcommand{\namefont}{\LARGE\bfseries}
\newcommand{\sectionfont}{\fontsize{11.2}{11.8}\selectfont\bfseries\scshape}
\newcommand{\entryfont}{\fontsize{10.55}{10.95}\selectfont\bfseries}
\newcommand{\detailfont}{\fontsize{9.0}{9.8}\selectfont}
\newcommand{\rowgap}{\vspace{3.0pt}}
\newcommand{\sectiontopspace}{7.0pt}
\newcommand{\sectionbottomspace}{4.2pt}

\titleformat{\section}{\sectionfont}{}{0pt}{}[\vspace{-2pt}\titlerule]
\titlespacing*{\section}{0pt}{\sectiontopspace}{\sectionbottomspace}

\newcommand{\entry}[4]{%
  \begin{tabular*}{\textwidth}{@{}p{0.74\textwidth}@{\extracolsep{\fill}}r@{}}
    {\entryfont #1} & #2 \\
    \textit{#3} & \textit{#4}
  \end{tabular*}\par\rowgap
}

\newcommand{\detail}[1]{%
  {\detailfont #1}\par\rowgap
}

\newcommand{\publication}[2]{%
  \begin{tabular*}{\textwidth}{@{}p{0.81\textwidth}@{\extracolsep{\fill}}r@{}}
    #1 & \textit{#2}
  \end{tabular*}\par\rowgap
}

\newcommand{\talk}[3]{%
  \begin{tabular*}{\textwidth}{@{}p{0.21\textwidth}@{\extracolsep{\fill}}p{0.54\textwidth}@{\extracolsep{\fill}}>{\raggedleft\arraybackslash}p{0.20\textwidth}@{}}
    {\entryfont #1} & #2 & \textit{#3}
  \end{tabular*}\par\rowgap
}

\newcommand{\datedline}[2]{%
  \begin{tabular*}{\textwidth}{@{}p{0.86\textwidth}@{\extracolsep{\fill}}r@{}}
    #1 & #2
  \end{tabular*}\par\rowgap
}

\newcommand{\plainline}[2]{%
  \textbf{#1:} #2\par\rowgap
}

\begin{document}
\fontsize{10.15}{10.95}\selectfont

\begin{center}
  {\namefont Javier Abad Martínez}\\[2pt]
  PhD Student in Machine Learning, ETH AI Center\\[1pt]
  \href{mailto:javier.abadmartinez@ai.ethz.ch}{javier.abadmartinez@ai.ethz.ch}
  \quad \href{https://jaabmar.github.io}{jaabmar.github.io}
  \quad \href{https://scholar.google.es/citations?user=gGHkUhkAAAAJ&hl=es}{Google Scholar}
  \quad \href{https://github.com/jaabmar}{GitHub}
  \quad \href{https://www.linkedin.com/in/javiabadm/}{LinkedIn}
\end{center}
\vspace{-7pt}

\section*{Research Interests}
Language model safety and alignment; privacy-preserving machine learning; causal inference.

\section*{Education}
\entry{ETH Zurich}{Dec. 2022 -- Jul. 2026}{PhD in Machine Learning; advised by Prof. \href{https://sml.inf.ethz.ch/group/fannyy/}{Fanny Yang}}{Zurich, Switzerland}
\detail{ETH AI Center Doctoral Fellow; Simons Institute visitor (UC Berkeley), Fall 2024; \href{https://digital-strategy.ec.europa.eu/en/policies/contents-code-gpai}{GPAI Code of Practice} expert group member.}
\entry{University of Cambridge}{Oct. 2020 -- Aug. 2021}{MPhil in Machine Learning and Machine Intelligence; awarded with Distinction}{Cambridge, UK}
\entry{Universidad Politécnica de Valencia}{Sep. 2015 -- Jul. 2020}{BSc in Telecommunications Engineering; BSc in Business Administration}{Valencia, Spain}
% \detail{GPAs: Telecommunications 96\%; Business 95\%; Georgia Tech exchange 4.0/4.0.}

\section*{Research Experience}
\entry{Google DeepMind}{Oct. 2025 -- Dec. 2025}{PhD Student Researcher, Gemma Post-training Team}{Zurich, Switzerland}
\entry{Apple}{Mar. 2025 -- Oct. 2025}{Machine Learning Researcher, Visual Generation \& AI Safety}{Cupertino, CA / Zurich}
\entry{Featurespace}{Mar. 2022 -- Nov. 2022}{Research Scientist}{London, UK}
\entry{University of Cambridge}{Oct. 2021 -- Feb. 2022}{Research Assistant, Machine Learning Group (\href{https://cbl.eng.cam.ac.uk/}{CBL}) with \href{https://mlg.eng.cam.ac.uk/adrian/}{Adrian Weller MBE}}{Cambridge, UK}
\entry{University of Cambridge}{Apr. 2021 -- Aug. 2021}{Research Assistant, Van der Schaar Lab with Prof. \href{https://www.vanderschaar-lab.com/prof-mihaela-van-der-schaar/}{Mihaela van der Schaar}}{Cambridge, UK}
\entry{Universidad Politécnica de Valencia}{Nov. 2019 -- Jul. 2020}{Research Assistant, Computer Vision \& Behavior Analysis Lab}{Valencia, Spain}

\section*{Selected Publications}
\publication{\href{https://arxiv.org/abs/2502.04262}{Efficient Randomized Experiments Using Foundation Models}}{NeurIPS 2025}
\publication{\href{https://arxiv.org/abs/2412.06619}{Copyright-Protected Language Generation via Adaptive Model Fusion}}{ICLR 2025, Oral}
\publication{\href{https://arxiv.org/abs/2401.17823}{Privacy-Preserving Data Release via Optimal Transport and Particle Gradient Descent}}{ICML 2024}
\publication{\href{https://arxiv.org/abs/2404.18905}{Detecting Critical Treatment Effect Bias in Small Subgroups}}{UAI 2024}
\publication{\href{https://arxiv.org/abs/2312.03871}{Hidden Yet Quantifiable: Lower Bounds for Confounding Strength}}{AISTATS 2024}
\publication{\href{https://arxiv.org/abs/2202.01315}{Approximating Full Conformal Prediction at Scale via Influence Functions}}{AAAI 2023, Oral}

\section*{Selected Talks}
\talk{Google DeepMind}{Inference-time compute for student--teacher distillation}{Zurich, 2025}
\talk{Apple}{Pre-training visual generation models}{Zurich, 2025}
\talk{ICLR 2025}{Adaptive model fusion for copyright protection}{Singapore, 2025}
\talk{Hasler Foundation}{Reliable inference from observational data}{Bern, 2024}
\talk{ETH AI Center}{Lower bounds for hidden confounding strength}{Zurich, 2024}
\talk{AAAI 2023}{Scaling conformal prediction with influence functions}{Washington, DC, 2023}

\section*{Awards and Fellowships}
\datedline{Excellence Fellowship in the Valencian Community}{2023}
\datedline{Best Engineering Graduate, Capitanía General de Valencia}{2022}
\datedline{ETH AI Center Doctoral Fellowship}{2022}
\datedline{``La Caixa'' Excellence Fellowship (declined)}{2021}
\datedline{Best Graduate, Telecommunications Engineering and Business Administration (separate awards)}{2021}
\datedline{First place, Spanish national ranking of Telecommunications Engineering students}{2021}

\section*{Skills and Languages}
\plainline{Technical}{Python, PyTorch, JAX, TensorFlow, Triton, MATLAB.}
\plainline{Languages}{Spanish and Catalan (native); English (fluent, C2); German (B1).}

\end{document}
